---
title: "midterm-2"
output: html_notebook
---
#midTerm2
```{r}
library(lubridate); library(stringr); library(purrr); library(readr);
```
#1.1
```{r}
homeworkData <- data.frame(
  姓名 = c("小明","小花","小新"),
  作業1分數 = c(10,9,5),
  作業2分數 = c(10,10,9),
  stringsAsFactors = F
)
```

#1.2
emailText <-
  "親愛的student好，您的作業成績為：作業1, y1分; 作業2, y2分"
```{r}
email_content_fun <- function(input){
  emailText <- str_c("親愛的student好，您的作業成績為：","作業1,",input["作業1分數"],
                     ",作業2,",input["作業2分數"])
  return(emailText)
}
```

```{r}
email_content_fun(homeworkData[3,])
```
##MTanswer
```{r}
email_content_fun1 <- function(input){
  emailText <-
  "親愛的student好，您的作業成績為：作業1, y1分; 作業2, y2分"
  str_replace(emailText, "student", input$姓名) -> emailTextOut
  str_replace(emailTextOut,"y1", as.character(input$作業1分數)) -> emailTextOut
  str_replace(emailTextOut,"y2", as.character(input$作業2分數)) -> emailTextOut
  return(emailTextOut)
}


```

```{r}
email_content_fun1(homeworkData[1,])
```
```{r}
homeworkData[1,]$姓名
```
#2
```{r}
str_smallClosest <- function(chrNumber,criticalNumber){
  as.numeric(chrNumber) -> NumchrNumber
  NumchrNumber <= criticalNumber -> MaxLogi
  max(chrNumber[MaxLogi]) -> AnsMax
  return(AnsMax)
  } 
```


```{r}
str_smallClosest(c(1,2,8),4)
```


#3.1
```{r}
list(
  "101"=list(url="http://www.econ.ntpu.edu.tw/econ/files/Way/2016072195021.doc"),
  "104"=list(url="http://www.econ.ntpu.edu.tw/econ/files/Way/2016072195041.doc"),
  "105"=list(url="http://www.econ.ntpu.edu.tw/econ/files/Way/20170516144353.doc"),
  "107"=list(url="http://www.econ.ntpu.edu.tw/econ/files/Way/20180518121643.pdf")
  )->EconCourseSelectionInfo
EconCourseSelectionInfo
```

```{r}
EconCourseSelectionInfo[["101"]]$url
```

#4

```{r}
load(url("https://www.dropbox.com/s/mk2zmcc2wjkwf7w/invoiceList.Rda?raw=true"))
c('訂單時區','訂單時間(以訂單時區顯示)','UTC時間') -> names(invoiceList)
```

```{r}
i <- 1
with_tz(
    ymd_hms(invoiceList$`訂單時間(以訂單時區顯示)`[[i]], tz = invoiceList$訂單時區[[i]]), 
    tzone = "UTC")
```
##??
```{r}
 with_tz(
    ymd_hms(invoiceList$`訂單時間(以訂單時區顯示)`[[1]], tz = "UTC"), 
    tzone = invoiceList$訂單時區[[1]]
    )
```


```{r}
for(i in seq_along(invoiceList)){
  with_tz(
    ymd_hms(invoiceList$`訂單時間(以訂單時區顯示)`[[i]], tz = invoiceList$訂單時區[[i]]), 
    tzone = "UTC"
    )  -> invoiceList$UTC時間[[i]]
}
```
##MTanswer
```{r}
(invoiceList$訂單時區=="America/New_York") -> nyLogical
(invoiceList$訂單時區=="Asia/Taipei") -> tpLogical

invoiceList$UTC時間[nyLogical] <-
  with_tz(ymd_hms(invoiceList$`訂單時間(以訂單時區顯示)`[nyLogical],
          tz="America/New_York"),tzone="UTC")
invoiceList$UTC時間[tpLogical] <-
  with_tz(ymd_hms(invoiceList$`訂單時間(以訂單時區顯示)`[tpLogical],
          tz="Asia/Taipei"),tzone="UTC")

```


#5
```{r}
load(url("https://www.dropbox.com/s/j4k4por0rl6s317/sampledTranscriptData.Rda?raw=true"))
c('學號','學期成績','學分數','學年','學期','必選修類別（必／選／通）','系級','科目名稱','年級','學屆') ->
  names(sampledTranscriptData)
```

```{r}
 str_sub(sampledTranscriptData$學號,5,6) != 73 & str_detect(sampledTranscriptData$系級,"經濟") -> 
 transferLogi
 sum(transferLogi)
 unique(sampledTranscriptData$學號[transferLogi]) -> changeMajorStudent
```

#Final
```{r}
library(lubridate); library(stringr); library(purrr); library(readr);
load(url("https://www.dropbox.com/s/8fcueq17vsy25cc/finalExam107-2.Rda?raw=1"))
```
##1
```{r}
str_smallClosest <- function(chrNumber,criticalNumber){
  as.numeric(chrNumber)->NumchrNumber
  max(chrNumber[NumchrNumber <= criticalNumber]) -> AnsMax
  return(AnsMax)
}
```

```{r}
str_smallClosest(c("2","178","987"),456)-> MaxAns
class(MaxAns)
```


#3
```{r}
question1Data() -> question1DF
question1DF
```

```{r}
dateTimeLisbon <- vector("character", 10)
dateTimeLisbon
```

```{r}
as.character(ymd_hms(question1DF$date_time,tz ="Europe/Lisbon"))
```

```{r}
question1DF$time_zone == "Asia/Taipei" -> logiTP
question1DF$time_zone == "America/New_York" -> logiNY
dateTimeLisbon <- vector("character",length(question1DF$date_time))
dateTimeLisbon[logiTP] <-
  as.character(
    with_tz(
      ymd_hms(question1DF$date_time[logiTP],tz="Asia/Taipei"),
      tzone="Europe/Lisbon"
    )
  )
dateTimeLisbon[logiNY] <-
  as.character(
    with_tz(
      ymd_hms(question1DF$date_time[logiNY],tz="America/New_York"),
      tzone="Europe/Lisbon"
    )
  )

dateTimeLisbon
```

