---
title: "midterm-2"
output: html_notebook
---
#midTerm2
```{r}
library(lubridate); library(stringr); library(purrr); library(readr);
```
#1.1
```{r}
homeworkData <- data.frame(
  姓名 = c("小明","小花","小新"),
  作業1分數 = c(10,9,5),
  作業2分數 = c(10,10,9),
  stringsAsFactors = F
)
```

#1.2
emailText <-
  "親愛的student好，您的作業成績為：作業1, y1分; 作業2, y2分"
```{r}
email_content_fun <- function(input){
  emailText <- str_c("親愛的student好，您的作業成績為：","作業1,",input["作業1分數"],
                     ",作業2,",input["作業2分數"])
  return(emailText)
}
```

```{r}
email_content_fun(homeworkData[3,])
```
##MTanswer
```{r}
email_content_fun1 <- function(input){
  emailText <-
  "親愛的student好，您的作業成績為：作業1, y1分; 作業2, y2分"
  str_replace(emailText, "student", input$姓名) -> emailTextOut
  str_replace(emailTextOut,"y1", as.character(input$作業1分數)) -> emailTextOut
  str_replace(emailTextOut,"y2", as.character(input$作業2分數)) -> emailTextOut
  return(emailTextOut)
}


```

```{r}
email_content_fun1(homeworkData[1,])
```
```{r}
homeworkData[1,]$姓名
```
#2
```{r}
str_smallClosest <- function(chrNumber,criticalNumber){
  as.numeric(chrNumber) -> NumchrNumber
  NumchrNumber <= criticalNumber -> MaxLogi
  max(chrNumber[MaxLogi]) -> AnsMax
  return(AnsMax)
  } 
```


```{r}
str_smallClosest(c(1,2,8),4)
```


#3.1
```{r}
list(
  "101"=list(url="http://www.econ.ntpu.edu.tw/econ/files/Way/2016072195021.doc"),
  "104"=list(url="http://www.econ.ntpu.edu.tw/econ/files/Way/2016072195041.doc"),
  "105"=list(url="http://www.econ.ntpu.edu.tw/econ/files/Way/20170516144353.doc"),
  "107"=list(url="http://www.econ.ntpu.edu.tw/econ/files/Way/20180518121643.pdf")
  )->EconCourseSelectionInfo
EconCourseSelectionInfo
```

```{r}
EconCourseSelectionInfo[["101"]]$url
```

#4

```{r}
load(url("https://www.dropbox.com/s/mk2zmcc2wjkwf7w/invoiceList.Rda?raw=true"))
c('訂單時區','訂單時間(以訂單時區顯示)','UTC時間') -> names(invoiceList)
```

```{r}
i <- 1
with_tz(
    ymd_hms(invoiceList$`訂單時間(以訂單時區顯示)`[[i]], tz = invoiceList$訂單時區[[i]]), 
    tzone = "UTC")
```
##??
```{r}
 with_tz(
    ymd_hms(invoiceList$`訂單時間(以訂單時區顯示)`[[1]], tz = "UTC"), 
    tzone = invoiceList$訂單時區[[1]]
    )
```


```{r}
for(i in seq_along(invoiceList)){
  with_tz(
    ymd_hms(invoiceList$`訂單時間(以訂單時區顯示)`[[i]], tz = invoiceList$訂單時區[[i]]), 
    tzone = "UTC"
    )  -> invoiceList$UTC時間[[i]]
}
```
##MTanswer
```{r}
(invoiceList$訂單時區=="America/New_York") -> nyLogical
(invoiceList$訂單時區=="Asia/Taipei") -> tpLogical

invoiceList$UTC時間[nyLogical] <-
  with_tz(ymd_hms(invoiceList$`訂單時間(以訂單時區顯示)`[nyLogical],
          tz="America/New_York"),tzone="UTC")
invoiceList$UTC時間[tpLogical] <-
  with_tz(ymd_hms(invoiceList$`訂單時間(以訂單時區顯示)`[tpLogical],
          tz="Asia/Taipei"),tzone="UTC")

```


#5
```{r}
load(url("https://www.dropbox.com/s/j4k4por0rl6s317/sampledTranscriptData.Rda?raw=true"))
c('學號','學期成績','學分數','學年','學期','必選修類別（必／選／通）','系級','科目名稱','年級','學屆') ->
  names(sampledTranscriptData)
```

```{r}
 str_sub(sampledTranscriptData$學號,5,6) != 73 & str_detect(sampledTranscriptData$系級,"經濟") -> 
 transferLogi
 sum(transferLogi)
 unique(sampledTranscriptData$學號[transferLogi]) -> changeMajorStudent
```

#Final
```{r}
library(lubridate); library(stringr); library(purrr); library(readr);
load(url("https://www.dropbox.com/s/8fcueq17vsy25cc/finalExam107-2.Rda?raw=1"))
```
##1
```{r}
str_smallClosest <- function(chrNumber,criticalNumber){
  as.numeric(chrNumber)->NumchrNumber
  max(chrNumber[NumchrNumber <= criticalNumber]) -> AnsMax
  return(AnsMax)
}
```

```{r}
str_smallClosest(c("2","178","987"),456)-> MaxAns
class(MaxAns)
```


#3
```{r}
question1Data() -> question1DF
question1DF
```

```{r}
dateTimeLisbon <- vector("character", 10)
dateTimeLisbon
```

```{r}
i <- 1
with_tz(ymd_hms(question1DF$date_time[[i]], tz=question1DF$time_zone[[i]]), tzone ="Europe/Lisbon")
```

```{r}
for(i in seq_along(question1DF)){
  with_tz(
    ymd_hms(
      question1DF$date_time[[i]], tz=question1DF$time_zone[[i]]), tzone ="Europe/Lisbon"
    )-> dateTimeLisbon[[i]]

}
dateTimeLisbon
```
##false
```{r}
as.character(ymd_hms(question1DF$date_time,tz ="Europe/Lisbon"))
```
##MTans
```{r}
question1DF$time_zone == "Asia/Taipei" -> logiTP
question1DF$time_zone == "America/New_York" -> logiNY
dateTimeLisbon1 <- vector("character",length(question1DF$date_time))
dateTimeLisbon1[logiTP] <-
  as.character(
    with_tz(
      ymd_hms(question1DF$date_time[logiTP],tz="Asia/Taipei"),
      tzone="Europe/Lisbon"
    )
  )
dateTimeLisbon1[logiNY] <-
  as.character(
    with_tz(
      ymd_hms(question1DF$date_time[logiNY],tz="America/New_York"),
      tzone="Europe/Lisbon"
    )
  )

dateTimeLisbon1
```




```{r}
question2DF <- question2Data()
```
#4
```{r}
question2DF <- question2Data()
```

```{r}
tzchange <- function(chrDateTimeInput,fromTz,toTz){
  with_tz(ymd_hms(chrDateTimeInput, tz = fromTz), tzone = toTz)-> toTzNum
  as.character(toTzNum) -> toTzNum
  return(toTzNum)
}
```

```{r}
tzchange(question2DF$date_time[[1]],question2DF$time_zone[[1]],"Europe/Lisbon")
```

```{r}
  dateTimeLisbon2 <- vector("character", length(question2DF$date_time))


for(i in seq_along(question2DF$date_time)){
  tzchange(question2DF$date_time[[i]],question2DF$time_zone[[i]],"Europe/Lisbon")->dateTimeLisbon2[[i]]
  
}
```

```{r}
dateTimeLisbon2[[1]]
```


```{r}
seq_along(question2DF)
```
##MTans
```{r}
levels(as.factor(question2DF$time_zone))-> allTzones
dateTimeLisbon2MT <- vector("character",length(question2DF$date_time))
for(i in seq_along(allTzones)){
  #i<-1
  question2DF$time_zone==allTzones[[i]] -> logiTZ_i  #time_zone 依樣的就可以一起動作!
  tzchange(question2DF$date_time[logiTZ_i],
           allTzones[[i]],
           "Europe/Lisbon") -> dateTimeLisbon2MT[logiTZ_i]
}

```

```{r}
length(allTzones)
```

```{r}
load(url("https://www.dropbox.com/s/t148l8bflvubyhm/GA.Rda?raw=1"))
```



```{r}
numRow <- vector("integer", 9)

for(i in seq_along(
  user_report_exportStudent[["dates"]][["sessions"]])
  ){
  nrow(
    user_report_exportStudent[["dates"]][["sessions"]][[i]]
    )->numRow[[i]]
}
```

```{r}
sum(numRow) -> totalClicks
```


```{r}
user_report_exportDesktop[["dates"]][["sessions"]][[9]]$activities[[1]]$details[[1]]$`Page URL`


```


```{r}
user_report_exportDesktop[["dates"]][["sessions"]][[1]]$activities[[1]]$details -> details1

details1[[1]]$`Page URL`[[1]] -> session6_act1_url

session6_act1_url
```
```{r}
testVect <- vector("character", 2)
i <- 1
activity <- user_report_exportDesktop[["dates"]][["sessions"]][[2]]$activities
for(i in seq_along(activity)){
  activity[[i]]$details[[1]]$`Page URL`-> testVect[[i]]
  }
```

```{r}
testVect
```

```{r}
activityURL_find <- function(activity){
  urlVect <- vector("character", length(activity))
  for(i in seq_along(activity)){
  activity[[i]]$details[[1]]$`Page URL`[[1]]->urlVect[[i]]
  }
  return(urlVect)
  }
```

```{r}
length(user_report_exportDesktop[["dates"]][["sessions"]][[2]]$activities)
```

```{r}
activityURL_find(user_report_exportDesktop[["dates"]][["sessions"]][[4]]$activities)
```
```{r}
length(user_report_exportDesktop[["dates"]][["sessions"]])
seq_along(user_report_exportDesktop[["dates"]]$sessions)
```

```{r}
allURL <- vector("list", length(user_report_exportDesktop[["dates"]][["sessions"]]))

for(i in seq_along(user_report_exportDesktop[["dates"]]$sessions)){
  activityURL_find(user_report_exportDesktop[["dates"]][["sessions"]][[i]]$activities)-> allURL[[i]]
}
```

```{r}
unlist(allURL)->allURLs_chr
```

```{r}
str_replace_all(allURLs_chr,"/course-107-2-learning-progress/","")->sha1
str_replace_all(sha1,".html","")->sha2
```

```{r}
unique(sha2) -> sha3
```

```{r}
sha2
```


```{r}
str_replace_all(allURLs_chr,"/course-107-2-learning-progress/","")->sha1
str_replace_all(sha1,".html","")->sha2
```




```{r}
table(sha2)
```
```{r}
table(sha2)[["1f5b2ca6c"]]
```
```{r}
visitCount_fun <- function(sha){
  table(sha2)[[sha]]
}
```


```{r}
visitCount_fun("1f5b2ca6c")
```
```{r}
visitCountVect <- vector("integer", length(sha3))
for(i in seq_along(sha3)){
  visitCount_fun(sha3[[i]])-> visitCountVect[[i]]
}
```

```{r}
visitCountVect
```

```{r}
sha3
```


```{r}

data.frame(
  sha = sha3,
  visit_count = visitCountVect,
  stringsAsFactors = F
)
```
##ansMT
```{r}
table(allURLs_chr) -> tb_allURLs
names(tb_allURLs) -> urlNames
str_replace_all(urlNames, 
                c("/course-107-2-learning-progress/"="",
                  ".html"="")) -> shaValues
df_teacherVisits <- data.frame(
  sha=shaValues,
  visit_count=as.integer(tb_allURLs),
  stringsAsFactors = F
)

df_teacherVisits
```


```{r}
shaValues
```
```{r}
urlNames
```

