---
title: "ntpu_programming_for_data_science-2"
output: html_notebook
---

#setup

```{r}
library(readr); library(dplyr); library(stringr); library(lubridate)
```

#Function and Conditional Execution

```{r}
utility_cobb_douglass <- function(x,y,.alpha,.beta){
  utilValue <- x^.alpha*y^.beta # 程序產生output值
  return(utilValue) # 傳回output值
}
```
```{r}
class(utility_cobb_douglass)
```
```{r}
utility_cobb_douglass(1,2,0.5,0.5)
```
```{r}
functionExemple <- function(x, alpha){
  return(x+alpha)
}
```
```{r}
functionExemple(1,1111)
```
 
```{r}
supply_fun <- function(a,b,P){
  Qs <- a+b*P
  return(Qs)
}
```
 
```{r}
demand_fun <- function(c,d,P){
  Qd <-  c-d*P
  return(Qd)
}
```

```{r}
demand_fun(5,1,1) - supply_fun(0,1,1)
```
```{r}
library(readr)
transcriptDataFinal <- read_csv("https://raw.githubusercontent.com/tpemartin/github-data/master/transcriptDataFinal.csv")
```

Input = studentID , Output = GPA
```{r}
studentID <-"92aS67fee" 
transcriptDataFinal$學號==studentID -> logiChosenStudent

subSample <- transcriptDataFinal[logiChosenStudent,]

sum(subSample$學期成績*subSample$學分數)/
  sum(subSample$學分數) -> GPA
GPA
```

```{r}
gpa_fun <- function(studentID){
  transcriptDataFinal$學號==studentID -> logiChosenStudent

subSample <- transcriptDataFinal[logiChosenStudent,]

sum(subSample$學期成績*subSample$學分數)/
  sum(subSample$學分數) -> GPA
  return(GPA)
}
```

```{r}
gpa_fun("d55S6d052")
```



#??????
```{r}
gpa_fun(transcriptDataFinal$學號)

```


```{r}
library(stringr)
sample(99:103,15,replace = T)-> yy
sample(1:12,15,replace=T)-> mm
str_c("民國",str_pad(yy,3,"left","0"),"年",mm,"月") -> twDates
```


```{r}
library(stringr); library(lubridate)
yyyy<-as.integer(str_extract(twDates,"(?<=(民國))[:digit:]+"))+1911
mm<-str_extract(twDates,"[:digit:]+(?=月)")
yyyymmdd <- ymd(str_c(yyyy,mm,"01",sep="-"))
```

```{r}
date_convert_twYM <- function(twDates){
  yyyy<-as.integer(str_extract(twDates,"(?<=(民國))[:digit:]+"))+1911
mm<-str_extract(twDates,"[:digit:]+(?=月)")
yyyymmdd <- ymd(str_c(yyyy,mm,"01",sep="-"))
return(yyyymmdd)
}
```

```{r}
date_convert_twYM(twDates)
```
America/NewYork "1973-02-21 12:05:22"時區轉換成Aisa/Taipei
```{r}
ymd_hms("1973-02-21 12:05:22", tz="America/New_York") -> NYTime
NYTime
with_tz(NYTime, tzone = "Asia/Taipei")
```
想像成function
("1973-02-21 12:05:22","America/New_York","Asia/Taipei")
為input

```{r}
ymd_hms_tzChange <- function(Time,tz1,tz2){
  ymd_hms("Time", tz="tz1") -> TimeDate
  with_tz(TimeDate, tzone = "tz2")-> tzChangeDate
  return(tzChangeDate)
}
```


```{r}
ymd_hms_tzChange("1973-02-21 12:05:22","America/New_York","Asia/Taipei")
```
```{r}
c("1973-02-21 12:05:22","1973-02-22 12:05:22")-> Exemple11
ymd_hms_tzChange(Exemple11, "America/New_York", "Asia/Taipei")
```
```{r}
utility_cobb_douglass2 <- function(x,y,.alpha=0.5,.beta=0.5){
  utilValue <- x^.alpha*y^.beta
  return(utilValue)
}
```


```{r}
utility_cobb_douglass2(1,2) # 使用預設值
utility_cobb_douglass2(1,2,0.5,0.8) # 自定參數值
```

```{r}
library(stringr); library(lubridate)
yyyy<-as.integer(str_extract(twDates,"(?<=(民國))[:digit:]+"))+1911
mm<-str_extract(twDates,"[:digit:]+(?=月)")
yyyymmdd <- ymd(str_c(yyyy,mm,"01",sep="-"))
```

```{r}
date_convert_twYM <- function(twDates, d = 1){
  yyyy<-as.integer(str_extract(twDates,"(?<=(民國))[:digit:]+"))+1911
mm<-str_extract(twDates,"[:digit:]+(?=月)")
yyyymmdd <- ymd(str_c(yyyy,mm,d,sep="-"))
return(yyyymmdd)
}
```

```{r}
date_convert_twYM("民國102年12月", 2)
```
```{r}
norm <- function(x) sqrt(x%*%x)
norm(1:4)
```
##函數程序並不一定要有return與input
```{r}
nowAnnounce <- function(){
  currentDateTime <- Sys.time()
  hh<-hour(currentDateTime)
  mm<-minute(currentDateTime)
  tz<-tz(currentDateTime)
  cat("現在是",hh,"點",mm,"分",tz)
}
```

```{r}
nowAnnounce()
```
```{r}
browseURL("https://www.ntpu.edu.tw")
```

```{r}
textBookURL <- function(){
  browseURL("https://www.ntpu.edu.tw")
}
```

```{r}
textBookURL()
```



```{r}
gpa_fun <- function(studentID){
  transcriptDataFinal$學號==studentID -> logiChosenStudent
  
  subSample <- transcriptDataFinal[logiChosenStudent,]
  
  sum(subSample$學期成績*subSample$學分數)/
    sum(subSample$學分數) -> GPA
  return(GPA)
}
```

```{r}
gpa_fun2 <- function(studentID){
  transcriptDataFinal$學號==studentID -> logiChosenStudent
  
  subSample <- transcriptDataFinal[logiChosenStudent,]
  
  sum(subSample$學期成績*subSample$學分數)/
    sum(subSample$學分數) -> GPA
  return(
    list(
      GPA,
      subSample
    )
  )
}
```

```{r}
gpa_fun2("92aS67fee") -> outputValue
outputValue$平均成績
outputValue$成績單
```


```{r}
gpa_fun2 <- function(studentID){
  transcriptDataFinal$學號==studentID -> logiChosenStudent
  
  subSample <- transcriptDataFinal[logiChosenStudent,]
  
  sum(subSample$學期成績*subSample$學分數)/
    sum(subSample$學分數) -> GPA
  return(
    list(
      平均成績=GPA,
      成績單=subSample
      )
  )
}
```

```{r}
gpa_fun2("92aS67fee") -> outputValue
outputValue$平均成績
```
```{r}
supply_fun <- function(a,b,P){
  Qs <- a+b*P
  return(Qs)
}
```
 
```{r}
demand_fun <- function(c,d,P){
  Qd <-  c-d*P
  return(Qd)
}
```


demand_supply_fun(P,a,b,c,d)

```{r}
demand_supply_fun <- function(P,a,b,c,d){
  Qs <-a+b*P
  Qd <-c-d*P
  ExcessSupply<- Qs-Qd
  return(
    list(
      供給量=Qs,
      需求量=Qd,
      超額供給=ExcessSupply
    )
  )
}
```

```{r}
demand_supply_fun(2,1,1,1,0.5)
```

#依條件執行


```{r}
supply_fun <- function(a,b,P){
  Qs <- a+b*P
  if(P>0){
    return(Qs)
  }
}
```

```{r}
supply_fun(1,1,-1)
```



```{r}
supply_fun2 <- function(P,a,b){
  Qs <- a+b*P
  if(P>=0) {
    return(Qs)
  }
}
supply_fun2(P=-1,0,1)
supply_fun2(P=2,0,1)
```

```{r}
supply_fun3 <- function(P,a,b){
  Qs <- a+b*P
  if(P < 0) {
    message("P不能為負值") # 在螢幕出現的「錯誤」提示，沒有輸出任何值
  } else {
    return(Qs)
  }
}
supply_fun3(P=-1,0,1)
supply_fun3(P=2,0,1)
```

```{r}
supply_fun4 <- function(P,a,b){
  Qs <- a+b*P
  if(P < 0) {
    message("P不能為負值") # 在螢幕出現的「錯誤」提示，沒有輸出任何值
  } else if(P < -a/b) {
    message("P必需大於等於",-a/b,"(即-a/b值)")
  } else {
    return(Qs)
  }
}
supply_fun4(P=-1,-3,1)
supply_fun4(P=2,-3,1)
supply_fun4(P=3,-3,1)
```

```{r}
library(readr)
transcriptDataFinal <- read_csv("https://raw.githubusercontent.com/tpemartin/github-data/master/transcriptDataFinal.csv")
```

```{r}
for(i in 1:5) print(1:i)
```

```{r}
for(n in c(2,5,10,20,50)) {
   x <- stats::rnorm(n)
   cat(n, ": ", sum(x^2), "\n", sep = "")
}
```

Implement a fizzbuzz function. It takes a single number as input. If the number is divisible by three, it returns “fizz”. If it’s divisible by five it returns “buzz”. If it’s divisible by three and five, it returns “fizzbuzz”. Otherwise, it returns the number. Make sure you first write working code before you create the function. –From, R for Data Science.
```{r}
fizzbuzz <- function(x){
  if(x%%3 == 0 & x%%5 !=0){
    print("fizz")
  }else if(x%%5==0 & x%%3 !=0){
      print("buzz")
  }else if(x%%5==0 & x%%3 ==0){
      print("fizzbuzz")
    }
}
```

```{r}
fizzbuzz(3)
fizzbuzz(5)
fizzbuzz(15)
```
所有的if邏輯條件產生值都必需是「單一」邏輯值
```{r}
a <- c(1,3,5)
a>2 # 此邏輯條件產生三個值
if(a>2) {
  print("a大於2")
}
```

```{r}
if(any(a>2))
  print("a>2")


```

```{r}
if(all(a>2))
  print("all a>2")else(
    print("not all a>2")
  )
```

#environment
```{r}
a <- 3

testfun <- function(x){
  y <- a/4
  output <- x*y
  return(output)
}

testfun(2)

a <- 4
testfun(2)
```

